Do return series have power-law tails with the same index?

### 2017-05-02 papers/FX/draft.tex
Corrected the proof of the monotonicity lemma.

\appendix
\section{A monontonicity lemma}
\begin{lemma} \label{lemma:I}
  Assume distribution function $F(x; \theta)$ parameterized by
  $\theta$ is defined on $x \in (a, b)$, $a, b \in \mathbb R \cup
  \{-\infty, \infty\}$, and in addition $F(x; \theta)$ has density
  function $f(x; \theta)$. Assume function $h(\cdot)$ is defined on
  $(a, b)$, $X \sim F$, $\text{supp}(X) = (a,b)$,
  $\E h(X) < \infty$ and
  \begin{eqnarray*}
    \left| \frac{\pd f(x, \theta)}{\pd \theta} \right| < \infty
    \quad \forall x \in (a, b)
  \end{eqnarray*}
  \begin{enumerate}
  \item If $h(\cdot)$ is decreasing and $\exists x_0 \in (a, b)$ such that
    $\frac{\pd f}{\pd \theta}(x_0; \theta) > 0$ on $(a, x_0)$ while
    $\frac{\pd f}{\pd \theta}(x_0; \theta) < 0$ on $(x_0, b)$, then
    \[
    \frac{\pd \E h(X)}{\pd \theta} > 0
    \]
  \item If $h(\cdot)$ is increasing and $\exists x_0 \in (a, b)$ such that 
    $\frac{\pd f}{\pd \theta}(x_0; \theta) < 0$ on $(a, x_0)$  while
    $\frac{\pd f}{\pd \theta}(x_0; \theta) > 0$ on $(x_0, b)$, then
    \[
    \frac{\pd \E h(X)}{\pd \theta} > 0
    \]
  \end{enumerate}
\end{lemma}
\begin{remark}
  \label{remark:I}
  Two other cases follow trivially from lemma \ref{lemma:I}:
  \begin{enumerate}
  \item If $h(\cdot)$ is increasing and $\frac{\pd f}{\pd \theta}$
    satisfies the
    same conditions of the 1st case of lemma \ref{lemma:I},
    $\frac{\pd \E h(X)}{\pd \theta} < 0$. This immediately follows
    from applying 1st case of lemma \ref{lemma:I} to $-h(\cdot)$.
  \item By the same argument, if $h(\cdot)$ is decreasing and
    ${\pd f \over \pd \theta}$ satisfies the same conditions of the
    2nd case of lemma \ref{lemma:I}, ${\pd \E h(X) \over \pd \theta} < 0$.
  \end{enumerate}
\end{remark}

\begin{proof}
  Clearly
  \begin{eqnarray*}
    && {\pd \E h(X) \over \pd \theta} \\
    &=& \int_a^b h(x) {\pd f \over \pd \theta}(x, \theta) dx \\
    &=& \underbrace{\int_a^{x_0} h(x) {\pd f \over \pd \theta}(x,
      \theta) dx}_{I_1}
    + \underbrace{\int_{x_0}^b h(x) {\pd f \over \pd \theta}(x,
      \theta) dx}_{I_2}
  \end{eqnarray*}
  \begin{enumerate}
  \item When $h(x)$ is decreasing on $(a, b)$ and ${\pd f \over \pd
    \theta}(x, \theta) > 0$ on $(a, x_0)$
    \[
    I_1 > h(x_0) \int_a^{x_0} {\pd f \over \pd \theta}(x, \theta) dx
    \]
    Similarly, because ${\pd f \over \pd \theta}(x, \theta) < 0$ for
    $x \in (x_0, b)$ and $h(x)$ is decreasing, we have
    \begin{eqnarray*}
      I_2 &=& \int_{x_0}^b -h(x_0)
      \left|{\pd f \over \pd \theta}(x, \theta) \right| dx \\
      &>& -h(x_0)
      \int_{x_0}^b \left| 
        {\pd f \over \pd \theta}(x, \theta)
      \right| dx
    \end{eqnarray*}
    Finally we have
    \begin{eqnarray*}
      {\pd \E h(X) \over \pd \theta}
      > h(x_0) \int_a^b {\pd f \over \pd \theta}(x, \theta) dx
      = h(x_0) {\partial \over \partial \theta} \int_a^b f(x, \theta) dx
      = 0
    \end{eqnarray*}
  \item If $h(\cdot)$ is increasing and $\exists x_0 \in (a, b)$ such that 
    ${\pd f \over \pd \theta}(x_0; \theta) < 0$ on $(a, x_0)$  while
    ${\pd f \over \pd \theta}(x_0; \theta) > 0$ on $(x_0, b)$
    \begin{eqnarray*}
      I_1 &=&
      \int_a^{x_0} -h(x)
      \left| {\pd f \over \pd \theta}(x, \theta) \right| dx \\
      &>&
      -h(x_0) \int_a^{x_0}
      \left| {\pd f \over \pd \theta}(x, \theta) \right| dx
    \end{eqnarray*}
    and obviously
    \[
    I_2 > h(x_0) \int_{x_0}^b
    {\pd f \over \pd \theta}(x, \theta) dx
    \]
    So
    \[
    {\pd \E h(X) \over \pd \theta}
    = I_1 + I_2
    > h(x_0) {\partial \over \partial \theta} \int_a^b f(x, \theta) dx = 0
    \]
  \end{enumerate}
\end{proof}

>>>>

\appendix
\section{A monontonicity lemma}
\begin{lemma} \label{lemma:I}
  Assume distribution function $F(x, \theta)$ parameterized by 
  $\theta \in \Theta$ is defined on $x \in (a, b)$,
  $a, b \in \mathbb R \cup \{-\infty, \infty\}$,
  and in addition $F(x, \theta)$ has density
  function $f(x, \theta)$ that is differentiable with respect to
  $\theta$ for all $\theta \in \Theta$.
  Moreover, $f(x, \theta)$ satisfies
  \begin{equation}\label{eq:frt}
  \int_a^b {\pd f(x, \theta) \over \pd \theta} dx
  < \infty
  \end{equation}
  Assume function $h(\cdot)$ is defined on
  $(a, b)$ and is monotonic throughout this interval;
  $X \sim F$ and $\E h(X) < \infty$. Then
  \begin{enumerate}
  \item If $h(\cdot)$ is decreasing and $\exists x_0 \in (a, b)$ such that
    $\frac{\pd f}{\pd \theta}(x_0, \theta) > 0$ on $(a, x_0)$ while
    $\frac{\pd f}{\pd \theta}(x_0, \theta) < 0$ on $(x_0, b)$, then
    \[
    \frac{\pd \E h(X)}{\pd \theta} > 0
    \]
  \item If $h(\cdot)$ is increasing and $\exists x_0 \in (a, b)$ such that 
    $\frac{\pd f}{\pd \theta}(x_0, \theta) < 0$ on $(a, x_0)$  while
    $\frac{\pd f}{\pd \theta}(x_0, \theta) > 0$ on $(x_0, b)$, then
    \[
    \frac{\pd \E h(X)}{\pd \theta} > 0
    \]
  \end{enumerate}
\end{lemma}
\begin{remark}
  \label{remark:I}
  Two other cases follow trivially from lemma \ref{lemma:I}:
  \begin{enumerate}
  \item If $h(\cdot)$ is increasing and $\frac{\pd f}{\pd \theta}$
    satisfies the
    same conditions of the 1st case of lemma \ref{lemma:I},
    $\frac{\pd \E h(X)}{\pd \theta} < 0$. This immediately follows
    from applying 1st case of lemma \ref{lemma:I} to $-h(\cdot)$.
  \item By the same argument, if $h(\cdot)$ is decreasing and
    ${\pd f \over \pd \theta}$ satisfies the same conditions of the
    2nd case of lemma \ref{lemma:I}, ${\pd \E h(X) \over \pd \theta} < 0$.
  \end{enumerate}
\end{remark}

\begin{proof}
  Firstly we show
  \[
    {\pd \over \pd \theta} \int_a^b f(x, \theta) dx
    =
    \int_a^b {\pd \over \pd \theta} f(x, \theta) dx    
  \]
  Let
  \[
  f_{\Delta}(x, \theta) = {
    f(x, \theta +  \Delta) - f(x, \theta)
    \over
    \Delta
  }
  \]
  Since $f(x, \theta)$ is differentiable for all $\theta \in \Theta$,
  \[
  f_{\Delta}(x, \theta) \to {\pd f \over \pd \theta}(x, \theta)
  \quad \Delta \to 0
  \]
  For any give $\epsilon > 0$ and sufficiently small
  $\Delta$, we have
  \[
  |f_{\Delta}(x, \theta)| <
  \left|
      {\pd f \over \pd \theta}(x, \theta)
  \right| (1 + \epsilon)
  \]
  Using \eqref{eq:frt} and dominated convergence theorem we obtain
  \[
  \lim_{\Delta \to 0} \int_a^b f_\Delta(x, \theta) dx
  =
  \int_a^b {\pd f \over \pd \theta}(x, \theta) dx
  < \infty
  \]
  That is
  \[
    {\pd \over \pd \theta} \int_a^b f(x, \theta) dx
    =
    \lim_{\Delta \to 0} {
      \int_a^b f(x, \theta + \Delta) dx
      -
      \int_a^b f(x, \theta) dx
      \over
      \Delta
    }
    =
    \int_a^b {\pd f \over \pd \theta}(x, \theta) dx     
  \]
  From \eqref{eq:frt} it easily follows that the set on which
  ${\pd f(x, \theta) \over \pd \theta} = \infty$ has Lesbegue
  measure 0. Call this set $S_0$. We have
  \begin{eqnarray*}
    && {\pd \E h(X) \over \pd \theta} \\
    &=& \int_{(a,b) \setminus S_0} h(x)
    {\pd f \over \pd \theta}(x, \theta) dx \\
    &=& \underbrace{\int_{(a, x_0) \setminus S_0}
      h(x) {\pd f \over \pd \theta}(x, \theta) dx}_{I_1}
    + \underbrace{\int_{(x_0, b) \setminus S_0}
      h(x) {\pd f \over \pd \theta}(x,
      \theta) dx}_{I_2}
  \end{eqnarray*}
  Moreover, $x_0$ being located in the interior of $(a, b)$ and
  $h(\cdot)$ being monotonic implies $h(x_0) < \infty$.
  \begin{enumerate}
  \item When $h(x)$ is decreasing on $(a, b)$ and ${\pd f \over \pd
    \theta}(x, \theta) > 0$ on $(a, x_0)$
    \[
    I_1 > h(x_0) \int_{(a, x_0) \setminus S_0}
    {\pd f \over \pd \theta}(x, \theta) dx
    \]
    Similarly, because ${\pd f \over \pd \theta}(x, \theta) < 0$ for
    $x \in (x_0, b)$ and $h(x)$ is decreasing, we have
    \begin{eqnarray*}
      I_2 &=& \int_{(x_0, b) \setminus S_0} -h(x_0)
      \left|{\pd f \over \pd \theta}(x, \theta) \right| dx
      > -h(x_0)
      \int_{(x_0, b) \setminus S_0} \left| 
        {\pd f \over \pd \theta}(x, \theta)
      \right| dx
    \end{eqnarray*}
    Finally we have
    \begin{eqnarray*}
      {\pd \E h(X) \over \pd \theta}
      > h(x_0) \int_{(a, b) \setminus S_0}
      {\pd f \over \pd \theta}(x, \theta) dx
      = h(x_0) {\partial \over \partial \theta}
      \int_{(a, b) \setminus S_0} f(x, \theta) dx
      = 0
    \end{eqnarray*}
  \item If $h(\cdot)$ is increasing and $\exists x_0 \in (a, b)$ such that 
    ${\pd f \over \pd \theta}(x_0, \theta) < 0$ on $(a, x_0)$  while
    ${\pd f \over \pd \theta}(x_0, \theta) > 0$ on $(x_0, b)$
    \begin{eqnarray*}
      I_1 &=&
      \int_{(a, x_0) \setminus S_0} -h(x)
      \left| {\pd f \over \pd \theta}(x, \theta) \right| dx
      >
      -h(x_0) \int_{(a, x_0) \setminus S_0}
      \left| {\pd f \over \pd \theta}(x, \theta) \right| dx
    \end{eqnarray*}
    and obviously
    \[
    I_2 > h(x_0) \int_{(x_0, b) \setminus S_0}
    {\pd f \over \pd \theta}(x, \theta) dx
    \]
    So
    \[
    {\pd \E h(X) \over \pd \theta}
    = I_1 + I_2
    > h(x_0) {\partial \over \partial \theta}
    \int_{(a, b) \setminus S_0} f(x, \theta) dx = 0
    \]
  \end{enumerate}
\end{proof}
